Optimal (Multiway) Spatial Joins

### 2024-05-25 msj.tex
yufei

The correctness of the algorithm follows from statements (b) and (2) of Lemma~\ref{lmm:hv:type1:properties}. Furthermore, if we are given $\contained_{R_{k-2}}(\bm{t})$ for each $\bm{t}$, statement (3) of assures us that the algorithm runs in $O(1 + |\J(R_1, ..., R_{k-3}, H', V)| + k \sum_\bm{t} |\contained_{R_{k-2}}(\bm{t})|) = O(1 + k \cdot \out)$ time.

>>>>

The correctness of the algorithm follows from statements (1) and (2) of Lemma~\ref{lmm:hv:type2:properties}. Furthermore, if we are given $\contained_{R_{k-2}}(\bm{t})$ for each $\bm{t}$, statement (3) of assures us that the algorithm runs in $O(1 + |\J(R_1, ..., R_{k-3}, H', V)| + k \sum_\bm{t} |\contained_{R_{k-2}}(\bm{t})|) = O(1 + k \cdot \out)$ time, where the derivation used Lemma~\ref{lmm:hv:type2:recur-output} and statement (3) of Lemma~\ref{lmm:hv:type2:properties}.
